Draft Visualizations for Semester Project

### 2018-11-30 Visualizations/Draft Visualizations Template.Rmd
Changes in the package loading
Removed package loading messages

#Loading the Data and Necessary Packages
```{r, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(comment = NA)
library(dplyr)
library(tidyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(knitr)
health <- read.csv("mentalsurvey_clean.csv")
```

>>>>

#Loading the Data and Necessary Packages
```{r, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(comment = NA)
library(dplyr)
library(tidyr)
library(ggplot2)
library(grid)
library(gridExtra)
library(knitr)
health <- read.csv("mentalsurvey_clean.csv")
```
